\documentclass{article}
%----------------------------------------------------------------------------------------
%	Param setting
%----------------------------------------------------------------------------------------
\setlength{\parindent}{0cm}
\setlength{\parskip}{1em}
\setlength{\itemsep}{0.5em}
\newcommand{\killinitspace}{-0.7em}

\usepackage{geometry}
\geometry{a4paper, margin={0.75in, 1in}}

\usepackage{enumitem}
\setitemize{itemsep=0em, topsep=0em, leftmargin=1.5em, label=$\diamond$}
\setenumerate{itemsep=0.5em, topsep=0em, leftmargin=2.5em}

\usepackage{titlesec}
\titleformat{\section}       % Customise the \section command 
  {\Large\scshape\raggedright} % Make the \section headers large (\Large),
  {}{0em}
  {}                 % Can be used to insert code before the heading
  [\titlerule \vspace{-0.7em}]       % Inserts a horizontal line after the heading

\usepackage{hyperref}

\usepackage{needspace}

\begin{document}
%----------------------------------------------------------------------------------------
%	Personal info
%----------------------------------------------------------------------------------------
{\Huge Yongho Shin}
\begin{itemize}[itemsep=-3pt, leftmargin=2.5pt, label=]
\item Postdoctoral researcher
\item Institute of Computer Science, University of Wrocław
\item ul. Joliot-Curie 15, 50-383 Wrocław,  Poland
\item Email: \texttt{yongho@cs.uni.wroc.pl}
\item Homepage: \texttt{https://yonghoshin36.github.io}
\end{itemize}

%----------------------------------------------------------------------------------------
%	Research interests
%----------------------------------------------------------------------------------------
\section{Research Interests}
Online/approximation/learning-augmented algorithms for combinatorial optimization problems

%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{Ph.D.~in Computer Science, Yonsei University, South Korea} \hfill Mar.~2018 -- Aug.~2024
\vspace{\killinitspace}
\begin{itemize}
\item Dissertation topic: Relaxing hard requirements of online optimization via learning augmentation and limited revocability
\item Advisor: Hyung-Chan An
\end{itemize}

\textbf{B.S.~in Computer Science, Yonsei University, South Korea} \hfill Mar.~2012 -- Feb.~2018
\vspace{\killinitspace}
\begin{itemize}
\item Awarded \textsl{high honors at graduation}
\end{itemize}

%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------
\section{Employment}
\textbf{Institute of Computer Science, University of Wrocław, Poland} \hfill Nov.~2024 -- present
\vspace{\killinitspace}
\begin{itemize}
\item Postdoctoral researcher
\item Advisor: Jarosław Byrka
\end{itemize}

%----------------------------------------------------------------------------------------
%	Research papers
%----------------------------------------------------------------------------------------
\section{Research Papers}
\begin{enumerate}[label={[\arabic*]}]
	\needspace{1\baselineskip}
	\item \label{shin2026omm} \textbf{Yongho Shin} and Phanu Vajanopath. Parsimonious learning-augmented online metric matching. \emph{Unpublished manuscript}, 2026. \textbf{To appear in ICML 2026.}
	
	\needspace{1\baselineskip}
	\item \label{abbasi2026flm} Fateme Abbasi, Martin Böhm, Jarosław Byrka, Matin Mohammadi, and \textbf{Yongho Shin}. Servicing matched client pairs with facilities. \emph{arXiv preprint arXiv:2602.19680}, 2026.
	
	\needspace{1\baselineskip}
	\item \label{choo2025matching} Davin Choo, Billy Jin, and \textbf{Yongho Shin}. Learning-augmented online bipartite fractional matching. \emph{arXiv preprint arXiv:2505.19252}, 2025. \textbf{Appeared at NeurIPS 2025.}

	\needspace{1\baselineskip}
	\item \label{lee2025ecc} Changyeol Lee, \textbf{Yongho Shin}, and Hyung-Chan An. Improved algorithms for overlapping and robust clustering of edge-colored hypergraphs: An LP-based combinatorial approach. \emph{arXiv preprint arXiv:2505.18043}, 2025. \textbf{Appeared at NeurIPS 2025.}

	\needspace{1\baselineskip}
	\item \label{shin2025ski} \textbf{Yongho Shin}, Changyeol Lee, Gukryeol Lee, and Hyung-Chan An. Improved learning-augmented algorithms for the multi-option ski rental problem via best-possible competitive analysis. \emph{ACM Transactions on Algorithms 22(1)}, 11:1--31, 2025. \emph{Conference version at ICML 2023~\ref{shin2023ski}.}
	
	\needspace{1\baselineskip}
	\item \label{abbasi2025ccc} Fateme Abbasi, Hyung-Chan An, Jaros{\l}aw Byrka, Changyeol Lee, and \textbf{Yongho Shin}. Chromatic correlation clustering via cluster LP. \emph{arXiv preprint arXiv:2510.13446}, 2025. 

	\needspace{1\baselineskip}
	\item \label{byrka2025setcover}  Jaros{\l}aw Byrka and \textbf{Yongho Shin}. Online rounding for set cover under subset arrivals. \emph{arXiv preprint arXiv:2507.13159}, 2025.

	\needspace{1\baselineskip}
	\item \label{shin2023ski2} \textbf{Yongho Shin}, Changyeol Lee, and Hyung-Chan An. On optimal consistency-robustness trade-off for learning-augmented multi-option ski rental. \emph{arXiv preprint arXiv:2312.02547}, 2023. \emph{Merged to \ref{shin2025ski}.}
	
	\needspace{1\baselineskip}
	\item \label{shin2023ski} \textbf{Yongho Shin}, Changyeol Lee, Gukryeol Lee, and Hyung-Chan An. Improved learning-augmented algorithms for the multi-option ski rental problem via best-possible competitive analysis. In \emph{Proceedings of the 40th International Conference on Machine Learning (ICML 2023)}, PMLR 202:31539-31561, 2023.

	\needspace{1\baselineskip}
	\item \label{kim2023pcfl} Kangsan Kim, \textbf{Yongho Shin}, and Hyung-Chan An. Constant-factor approximation algorithms for parity-constrained facility location and $k$-center. \emph{Algorithmica 85}, 1883–1911, 2023. \emph{Conference version at ISAAC 2020~\ref{kim2020pcfl}.}

	\needspace{1\baselineskip}
	\item \label{shin2021ocs} \textbf{Yongho Shin} and Hyung-Chan An. Making three out of two: Three-way online correlated selection. In \emph{Proceedings of the 32nd International Symposium on Algorithms and Computation (ISAAC 2021)}, 49:1-49:17, 2021.

	\needspace{1\baselineskip}
	\item \label{kim2020pcfl} Kangsan Kim, \textbf{Yongho Shin}, and Hyung-Chan An. Constant-factor approximation algorithms for the parity-constrained facility location problem. In \emph{Proceedings of the 31st International Symposium on Algorithms and Computation (ISAAC 2020)}, 21:1-21:17, 2020.
	
	\needspace{1\baselineskip}
	\item \label{shin2020matching} \textbf{Yongho Shin}, Kangsan Kim, Seungmin Lee, and Hyung-Chan An. Online graph matching problem with a worst-case reassignment budget. \emph{arXiv preprint arXiv:2003.05175}, 2020.
\end{enumerate}

%----------------------------------------------------------------------------------------
%	Teaching
%----------------------------------------------------------------------------------------
\section{Teaching}
University of Wrocław, Poland
\vspace{\killinitspace}
\begin{itemize}
\item Algorithms with predictions \hfill Summer 2026
\end{itemize}

\textsl{Teaching assistant}, Yonsei University, South Korea
\vspace{\killinitspace}
\begin{itemize}
\item CSI2103/CCO2103 Data structures \hfill Spring 2018 -- 2021, 2023, 2024
\item CSI3108 Algorithm analysis \hfill Fall 2018 -- 2021, 2023
\item AIC2130 Computer algorithms for AI applications \hfill Fall 2023
\item GEK6205 Design and analysis of optimization algorithms \hfill Fall 2023
\end{itemize}

%----------------------------------------------------------------------------------------
%	Awards
%----------------------------------------------------------------------------------------
\section{Awards}
\textsl{High honors at graduation}, Yonsei University \hfill Feb.~2018

%----------------------------------------------------------------------------------------
%	Service
%----------------------------------------------------------------------------------------
\section{Academic Service}
\begin{itemize}
\item Reviewer, IWOCA 2026
\item Reviewer, ICML 2026
\item Reviewer, Acta Informatica 2026
\item Program committee member, EC 2026
\item Reviewer, STOC 2026
\item Reviewer, APPROX 2025
\item Reviewer, ICALP 2025
\item Reviewer, Mathematical Programming 2024
\item Reviewer, WAOA 2024
\end{itemize}

%----------------------------------------------------------------------------------------
%	Presentations
%----------------------------------------------------------------------------------------
\section{Talks and Presentations}
\needspace{1\baselineskip}
\textsl{SNU Math Seminar}, SNU, Seoul, South Korea \hfill Jan.~2026
\vspace{\killinitspace}
\begin{itemize}
\item Title: Online rounding for set cover under subset arrivals
\end{itemize}

\needspace{1\baselineskip}
\textsl{Combinatorics Seminar}, Hanyang University, Seoul, South Korea \hfill Jan.~2026
\vspace{\killinitspace}
\begin{itemize}
\item Title: Primal-dual algorithms for edge-colored clustering
\end{itemize}

\needspace{1\baselineskip}
\textsl{SNU CSE Seminar}, SNU, Seoul, South Korea \hfill Dec.~2025
\vspace{\killinitspace}
\begin{itemize}
\item Title: Learning-augmented online bipartite fractional matching
\end{itemize}

\needspace{1\baselineskip}
\textsl{NeurIPS 2025}, San Diego, CA, USA \hfill Dec.~2025
\vspace{\killinitspace}
\begin{itemize}
\item Title: Improved algorithms for overlapping and robust clustering of edge-colored hypergraphs: An LP-based combinatorial approach
\item Poster presentation
\end{itemize}

\needspace{1\baselineskip}
\textsl{NeurIPS 2025}, San Diego, CA, USA \hfill Dec.~2025
\vspace{\killinitspace}
\begin{itemize}
\item Title: Learning-augmented online bipartite fractional matching
\item Poster presentation
\end{itemize}

\needspace{1\baselineskip}
\textsl{2025 Combinatorics Workshop}, IBS DIMAG, Daejeon, South Korea \hfill Aug.~2025
\vspace{\killinitspace}
\begin{itemize}
\item Title: Learning-augmented online bipartite fractional matching
\item Contributed talk
\end{itemize}

\needspace{1\baselineskip}
\textsl{DGIST BRL AGSTA Seminar}, DGIST, Daegu, South Korea \hfill Aug.~2025
\vspace{\killinitspace}
\begin{itemize}
\item Title: Online rounding for set cover under subset arrivals
\end{itemize}

\needspace{1\baselineskip}
\textsl{Discrete Analysis Seminar}, Yonsei University, Seoul, South Korea \hfill Aug.~2025
\vspace{\killinitspace}
\begin{itemize}
\item Title: Online rounding for set cover under subset arrivals
\end{itemize}

\needspace{1\baselineskip}
\textsl{Combinatorial Optimization Seminar}, Yonsei University, Seoul, South Korea  \hfill Aug.~2025
\vspace{\killinitspace}
\begin{itemize}
\item Title: Learning-augmented online bipartite fractional matching
\end{itemize}

\needspace{1\baselineskip}
\textsl{HALG 2025}, ETH Zurich, Zurich, Switzerland \hfill June~2025
\vspace{\killinitspace}
\begin{itemize}
\item Title: Learning-augmented algorithms for the multi-option ski rental problem
\item Contributed talk and poster presentation
\end{itemize}

\needspace{1\baselineskip}
\textsl{COG Seminar}, University of Wrocław, Wrocław, Poland  \hfill May~2025
\vspace{\killinitspace}
\begin{itemize}
\item Title: Learning-augmented online bipartite fractional matching
\end{itemize}

\needspace{1\baselineskip}
\textsl{COG Seminar}, University of Wrocław, Wrocław, Poland  \hfill Dec.~2024
\vspace{\killinitspace}
\begin{itemize}
\item Title: Online correlated selection
\end{itemize}

\needspace{1\baselineskip}
\textsl{Discrete Analysis Seminar,} Yonsei University, Seoul, South Korea \hfill June~2024
\vspace{\killinitspace}
\begin{itemize}
\item Title: Three-way online correlated selection
\end{itemize}

\needspace{1\baselineskip}
\textsl{Discrete Math Seminar}, IBS DIMAG, Daejeon, South Korea \hfill May~2024
\vspace{\killinitspace}
\begin{itemize}
\item Title: Three-way online correlated selection
\end{itemize}

\needspace{1\baselineskip}
\textsl{ICML 2023}, Honolulu, HI, USA \hfill July~2023
\vspace{\killinitspace}
\begin{itemize}
\item Title: Improved learning-augmented algorithms for the multi-option ski rental problem via best-possible competitive analysis
\item Poster presentation
\end{itemize}

\needspace{2\baselineskip}
\textsl{Theory Tea}, Cornell University, Ithaca, NY, USA \hfill Dec.~2022
\vspace{\killinitspace}
\begin{itemize}
\item Title: Three-way online correlated selection
\end{itemize}

\needspace{1\baselineskip}
\textsl{ISAAC 2021}, Fukuoka, Japan (virtual) \hfill Dec.~2021
\vspace{\killinitspace}
\begin{itemize}
\item Title: Making three out of two: Three-way online correlated selection
\end{itemize}

\needspace{1\baselineskip}
\textsl{AAAC 2021}, Tainan, Taiwan (virtual) \hfill Oct.~2021
\vspace{\killinitspace}
\begin{itemize}
\item Title: Making three out of two: Three-way online correlated selection
\end{itemize}

\needspace{1\baselineskip}
\textsl{ISAAC 2020}, Hong Kong, China (virtual) \hfill Dec.~2020
\vspace{\killinitspace}
\begin{itemize}
\item Title: Constant-factor approximation algorithms for the parity-constrained facility location problem
\end{itemize}


%----------------------------------------------------------------------------------------
%	Experience
%----------------------------------------------------------------------------------------
\section{Experience}
\needspace{1\baselineskip}
\textsl{Co-organizer} of Yonsei CS theory student group, Yonsei University, South Korea \hfill Jan.~2023 -- Feb.~2024
\vspace{\killinitspace}
\begin{itemize}
\item Initiated a reading group of TCS students in and out of Yonsei University
\item Organized seminar talks on various topics including mechanism design and quantum computing
\end{itemize}

\needspace{1\baselineskip}
\textsl{Intern}, Cornell University, USA \hfill Sept.~2022 -- Dec.~2022
\vspace{\killinitspace}
\begin{itemize}
\item Director: David B. Shmoys
\end{itemize}

\needspace{1\baselineskip}
\textsl{Undergraduate intern}, Yonsei University, South Korea \hfill Jan.~2017 -- Feb.~2018
\vspace{\killinitspace}
\begin{itemize}
\item Advisor: Hyung-Chan An
\end{itemize}

\needspace{1\baselineskip}
\textsl{Undergraduate voluntary tutor}, Yonsei University, South Korea
\vspace{\killinitspace}
\begin{itemize}
\item CSI3108 Algorithm analysis \hfill Fall 2016, 2017
\item CSI2103 Data structures \hfill Spring 2017
\end{itemize}

\needspace{1\baselineskip}
\textsl{Web programmer}, Republic of Korea Air Force, South Korea \hfill Nov.~2013 -- Aug.~2015
\vspace{\killinitspace}
\begin{itemize}
\item In fulfillment of mandatory military service
\end{itemize}
\end{document}