\documentclass{article}

\usepackage{kotex}

\usepackage{geometry}
\geometry{a4paper, margin={0.75in, 1in}}

\usepackage{enumitem}

\title{Research Statement}
\author{Yongho Shin}
\date{}
\begin{document}
\maketitle


\section{Learning-Augmented Online Optimization}
\begin{itemize}
\item Learning-augmented multi-option ski rental. \\
우리 성과\\
identifying the best possibility of the randomized learning-augmented algorithms\\
another application of the button problems

\item Parsimonious learning-augmented online metric matching.\\
임성진 교수님 논문 for learning-augmented caching, open question\\
metric matching/MTS로 확장 가능함

\item New error metric for online metric matching. \\
기존 online metric matching의 error metric \\
Azar et al.의 error metric \\
Combine these two
\end{itemize}

\section{Online Optimization}
\begin{itemize}
\item Online correlated selection.\\
Fahrbach et al., 우리 성과, Gao et al., Blanc \& Charikar 언급\\
Improve? any idea? \\
Another applications?

\item Online bipartite matching with worst-case reassignments.\\
Bernstein et al.에서 inspired?\\
Deterministic algorithm\\
Does randomization help?

\item Multi-stage bipartite matching.\\
Feng et al. two-stage, Feng \& N.. multi-stage fractional\\
Multi-stage integral? \\
For unweighted case, 이의웅 교수님 논문 + matching skeleton implies multi-stage integral algorithm; but only 3-stage gives a better-than-0.632. \\
Dependent rounding technique may help

\item Online weighted geometric set cover and hitting set.\\
SoCG 2023 논문 \& subsequent papers\\
weighted case, doubling scheme\\
laminar family, intervals, logarithmic-competitive for both problems\\
extend to a general problem? e.g., 2d-axis-parallel boxes, VC-dimension\\
cell complexity and divide-and-conquer-like approach may help?
\end{itemize}

\section{Approximation Algorithms}
\begin{itemize}
\item Edge-colored clustering with outliers.\\
Veldt's work\\
$r$ outliers for each hyperedge? LP-rounding algorithm, integrality gap of $O(r)$

\item Bottleneck asymmetric traveling salesman problem.\\
Thin tree for laminar families, and then?

\item Facility location for matched clients.\\
Parity-constrained facility location\\
what if clients should be matched in order to get assigned to a facility?\\
Other settings, e.g., dynamic or online?


\end{itemize}

\section{Others}
\begin{itemize}
\item Bandit learning for stable matching.\\
Kong and Li's player-optimal stable matching learning needs observations on the arms' decisions \\
remove these observations? using properties of Gale-Shapley's?

\item Bilateral trade with partial information.\\
Bilateral trade. When only the average of one distribution is known, 2/3 is achievable and the best possible.\\
What if stdev (and beyond) is also known?
\end{itemize}


\end{document}